### 2014-07-31 paper/paper.tex
Wrote a bunch more.

Draft 2 %TODO ditch this

@@

\newpage
%\pagestyle{headings}
\setcounter{page}{1}

@@

TODO establish baseline here

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c|c|r|r|r|r|}
        \hline
        Description & Stopwords & Run 1 & Run 2 & Run 3 & $\mu$ F\\
        \hline
        MaxEnt      & Yes       & 0.0   & 0.0   & 0     & 0 \\
        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
        Naive Bayes & Yes       & 0.0   & 0.0   & 0     & 0 \\
        \dots       & No        & 0.0   & 0.0   & 0     & 0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Results of variations on feature selection and training. Sorted by
        average F-score.}
    \label{table:results}
\end{table}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Team       & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        AMI\&ERIC  & 62.55 \\
        FBM        & 61.17 \\
        AVAYA      & 60.84 \\
        SAIL       & 60.14 \\
        UT-DB      & 59.87 \\
        FBK-irst   & 59.76 \\
        nlp.cs.aueb.gr & 58.91 \\
        UNITOR     & 58.27 \\
        LVIC-LIMSI & 57.14 \\
        Unigon     & 56.96 \\
        NILC\_USP  & 56.31 \\
        DataMining & 55.52 \\
        ECNUCS     & 55.05 \\
        nlp.cs.aueb.gr & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP   & 54.33 \\
        CodeX      & 53.89 \\
        Oasis      & 53.84 \\
        \textbf{Best MaxEnt}& \textbf{53.32} \\
        NTNU       & 53.23 \\
        UoM        & 51.81 \\
        SSA-UO     & 50.17 \\
        SenselyticTeam & 50.10 \\
        $\ldots$   & $\ldots$ \\
        9 more teams &  \textless\ 50 \\
        $\ldots$   & $\ldots$ \\
        \hline
        Majority Baseline & 29.19 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
        workshop. Sorted by F-score.}
    \label{table:comparison}
\end{table}

>>>>

Draft 3 %TODO ditch this

@@

\newpage
\setcounter{page}{1}

@@

The proceedings of SemEval-2013 establishes the `Majority Baseline' for the
task to be an F-score of 29.19. How this number is calculated is not discusses
in paper.

The baseline for this project is established by running the Maximum Entropy
classifier without any Stop word removal, Uncommon word removal, Or feature
Normalization. The F-score that is achieved is 50.72. See Experiment \textit{g}
in Table \ref{table:results} to see the results in context.

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||c|c|c|c|r|r|r|r|}
        \hline
                   & Classifier  & Stopwords & Uncommon  & Normalize & Run 1 & Run 2 & Run 3 & $\mu F$\\
        \hline
        \textit{a} & MaxEnt      & Yes       & Yes       & Yes       & 51.55 & 52.80 & 54.09 & 52.81 \\
        \textit{b} & \dots       & Yes       & Yes       & No        & 51.10 & 49.34 & 50.23 & 50.22 \\
        \textit{c} & \dots       & Yes       & No        & Yes       & 53.51 & 51.97 & 52.06 & 52.51 \\
        \textit{d} & \dots       & Yes       & No        & No        & 54.55 & 48.77 & 49.51 & 50.94 \\
        \textit{e} & \dots       & No        & Yes       & Yes       & 50.88 & 50.55 & 52.09 & 51.17 \\
        \textit{f} & \dots       & No        & Yes       & No        & 52.46 & 50.64 & 54.11 & 52.40 \\
        \textit{g} & \dots       & No        & No        & Yes       & 49.80 & 56.26 & 54.13 & 53.40 \\
        \textit{h} & \dots       & No        & No        & No        & 50.59 & 50.91 & 50.67 & 50.72 \\
        \textit{i} & Naive Bayes & Yes       & Yes       & Yes       & 50.89 & 50.34 & 51.64 & 50.96 \\
        \textit{j} & \dots       & Yes       & Yes       & No        & 48.56 & 46.99 & 51.01 & 48.85 \\
        \textit{k} & \dots       & Yes       & No        & Yes       & 51.55 & 51.22 & 49.79 & 50.85 \\
        \textit{l} & \dots       & Yes       & No        & No        & 47.03 & 50.45 & 49.01 & 48.83 \\
        \textit{m} & \dots       & No        & Yes       & Yes       & 47.95 & 51.91 & 49.67 & 49.36 \\
        \textit{n} & \dots       & No        & Yes       & No        & 47.88 & 50.02 & 48.78 & 48.89 \\
        \textit{o} & \dots       & No        & No        & Yes       & 50.09 & 50.83 & 51.77 & 50.90 \\
        \textit{p} & \dots       & No        & No        & No        & 51.15 & 50.05 & 47.27 & 49.49 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Results of variations on feature selection and training. The
    `Citation' column indicates what type of classifier is being used. The
    `Stopwords' column indicates if stop words have been removed. The `Uncommon'
    column indicates if words with a document frequency lower than the threshold
    (in this case more than one occurrence) have been removed. The `Normalize'
    column indicates if the any steps have been taken to normalize features.}
    \label{table:results}
\end{table}

The results in Table \ref{table:results} indicates that there is not lot of
difference variation between experiments. The best average F-score is
experiment \textit{g}, however $\sigma_{g} = 2.69$. In contrast, the second
best F-score is experiment \textit{a} exhibits more consistent classification
with $\sigma_{a} = 1.04$.

%TODO write about the number of features

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Team       & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        AMI\&ERIC  & 62.55 \\
        FBM        & 61.17 \\
        AVAYA      & 60.84 \\
        SAIL       & 60.14 \\
        UT-DB      & 59.87 \\
        FBK-irst   & 59.76 \\
        nlp.cs.aueb.gr & 58.91 \\
        UNITOR     & 58.27 \\
        LVIC-LIMSI & 57.14 \\
        Unigon     & 56.96 \\
        NILC\_USP  & 56.31 \\
        DataMining & 55.52 \\
        ECNUCS     & 55.05 \\
        nlp.cs.aueb.gr & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP   & 54.33 \\
        CodeX      & 53.89 \\
        Oasis      & 53.84 \\
        NTNU       & 53.23 \\
        \textbf{Best MaxEnt}& \textbf{52.81} \\
        UoM        & 51.81 \\
        \textbf{Best Navie Bayes}& \textbf{50.96} \\
        SSA-UO     & 50.17 \\
        SenselyticTeam & 50.10 \\
        $\ldots$   & $\ldots$ \\
        9 more teams &  \textless\ 50 \\
        \hline
        Majority Baseline & 29.19 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
        workshop. Sorted by F-score.}
    \label{table:comparison}
\end{table}
